\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{classic} % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault} % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc} % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8} % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.80]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm} % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\name{Paul}{Ashbourne}
\title{Paul Ashbourne Cover Letter}
\address{110 Orchard Heights Blvd.}{Aurora, Ontario}{Canada L4G 2Z9}
%\phone[mobile]{+1~(234)~567~890}
\phone[fixed]{(905) 758-2239}
%\phone[fax]{+3~(456)~789~012}
\email{paul.ashbourne@uwaterloo.ca}
%\homepage{www.johndoe.com}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}
%\quote{Some quote}

\begin{document}

\recipient{Dropbox Recruiting}{Dropbox, Inc.\\185 Berry St \#400\\San Francisco, California 94107}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}
%\enclosure[Attached]{curriculum vit\ae{}}
\makelettertitle

As a longtime user of Dropbox, I am always impressed with the effectiveness and simplicity of the cloud-storage platform.
Dropbox has changed the way that I interact with technology and how I store, access, and safeguard my digital life. I am
studying Software Engineering at the University of Waterloo in and am currently in my 3A school term.
I recently learned that Dropbox would be hiring interns for the summer of 2016 and am excited at the opportunity to apply
for this role.

I have spent my last two work terms interning at Wish, a rapidly-growing e-commerce startup in San Francisco.
As a member of Wish's platform team, I was responsible for maintaining the front-end and back-end systems of
the e-commerce platform and worked across the entire stack. In my time at Wish, I completed several successful
projects which had significant impact on the growth of the business. One such project required me to build a
system to automate pre-orders of popular products at bulk prices. This feature led to an increase of profit margins
from 15\% to 30\% on affected products. Another notable project which I owned across the entire stack was the
development of a system which leveraged a network of global warehouses to store products closer to customers,
significantly reducing shipping times. I also redesigned the merchant signup and onboarding flow from scratch,
leading to an increase in the end-to-end conversion rate by a factor of 6.

I am highly motivated and rapidly learn new skills on-demand. In my previous positions, I have been complimented
by my colleagues for consistently seeking ways to improve all features and systems that I work on and for
improving the efficiency of the entire team through my work. I am an excellent team player and work effectively
with individuals of varying backgrounds and technical expertise. I believe that my considerable technical skills,
coupled with my constant motivation to improve myself and everything that I work on, will make me a valuable asset
to the Dropbox team.

Thank you for taking the time to review my application. I look forward to speaking with you about how I can
apply my skills to contribute to the growth and success of Dropbox. Please contact me regarding interview
availability. I can be reached by phone at (905) 758-2239 or by email at paul.ashbourne@uwaterloo.ca.

\makeletterclosing\\
3A Software Engineering\\
University of Waterloo

\end{document}
